A hierarchical approach for modelling X-ray beamlines. Application to a coherent beamline.

### 2019-03-24 paper-hierarchical.tex
starting

>>>>

Many storage-ring based x-ray synchrotron facilities are building or planning upgrades to increase brilliance and coherent flux by one to three orders of magnitude.  The first upgrade of a large facility will be the EBS (Extremely Brilliant Source) \cite{orangebook} at the European Synchrotron Radiation Facility (ESRF), aiming to build a storage ring of 150 pm emittance to significantly boost the associated x-ray coherence. Applications exploiting beam coherence such as such as x-ray photon correlation spectroscopy, coherent diffraction imaging, propagation-based phase contrast imaging and ptychography will benefit from this update.

Accurate calculation and quantitative evaluation of the parameters related to x-ray coherence is of paramount importance for designing, building and exploiting the new beamlines.
